Faithful Variable Screening for\\ High-Dimensional Convex Regression

### 2015-05-18 tex/scam/experiments.tex
a

\subsubsection{First simulation}
In the \textrm{first simulation} (Figure~\ref{Support}a), we vary the ambient dimension $p$. We set $Q$ as one on the diagonal and $1/2$ on the off-diagonal with $0.5$ probability, set $s=5$, and $p=64,128,256$ and $512$. We draw $X \sim N(0, I_p)$.
For each $(n,p)$ combination, we generate $100$ independent trials. 
In Figure~\ref{Support}(a), we plot the probability of exact
support recovery. We observe that the algorithm performs consistent variable selection even if the dimensionality is large. To give the reader a
sense of the running speed, for a 
data set with $n=1000$ and $p=512$, the code runs in roughly two 
minutes on a machine with 2.3 GHz Intel Core i5 CPU and 4 GB memory.

>>>>

\subsubsection{First simulation}
In the \textrm{first simulation} (Figure~\ref{Support}a), we vary the
ambient dimension $p$. We set $Q$ to be one on the diagonal and $1/2$ on
the off-diagonal with $0.5$ probability, set $s=5$, and $p=64,128,256$
and $512$. We draw $X \sim N(0, I_p)$.  For each $(n,p)$ combination,
we generate $100$ independent trials.  In Figure~\ref{Support}(a), we
plot the probability of exact support recovery. We observe that the
algorithm performs consistent variable selection even if the
dimensionality is large. To give the reader a sense of the running
speed, for a dataset with $n=1,000$ and $p=512$, the code runs in
roughly two minutes on a machine with a 2.3 GHz Intel Core i5 CPU and 4
GB memory.
